### 2022-03-29 manuscript.tex
smaller [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/45ad3e1f82e23620299e097363b1c30494d03bfa.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/45ad3e1f82e23620299e097363b1c30494d03bfa/checks
https://github.com/scherzerthesis/thesis/actions/runs/2055692115

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/02d58ac3e5f0bd59f708837074746dc2eb309ec4/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/02d58ac3e5f0bd59f708837074746dc2eb309ec4}{scherzerthesis/thesis@02d58ac}
on March 29, 2022.

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/45ad3e1f82e23620299e097363b1c30494d03bfa/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/45ad3e1f82e23620299e097363b1c30494d03bfa}{scherzerthesis/thesis@45ad3e1}
on March 29, 2022.
